Multiband Periodograms of Astronomical Sources

### 2014-12-15 writeup/paper.tex
update discussion of weighting single fits

\section{Moving to Multiple Bands}

@@

\todo{Talk about the $N_{base} = 0$, $N_{band} = 1$ case. This is equivalent to fitting a floating-mean Lomb-Scargle independently to each band, and constructing a weighted sum of each individual periodogram.}

@@

>>>>

\section{A Multiple-Band Model}

@@

The final remaining piece is our assumption that the data are centered (i.e. \eq{ycentered}). This is required so that the simple form of the reference $\chi^2_0$ remains valid. For the multiband model, this assumption requires that the data satisfy \eq{ycentered} {\it within each band}.

\subsection{Relationship of Multiband and Single-band approaches}
There is a special case of the multi-band approach when $N_{base}=0$ and $N_{band}=1$. In this case, the $X$ matrix can be arranged to be block-diagonal, and the computation can be split into an independent single-band computation for each of the $K$ bands. For band $k$, denote the single-band periodogram as
\begin{equation}
  P_N^{(k)}(\omega) = 1 - \frac{\chi^2_{min, k}(\omega)}{\chi^2_{0,k}}
\end{equation}
The full multiband periodogram is given by
\begin{equation}
  P_N(\omega) = 1 - \frac{\sum_{k=1}^K\chi^2_{min, k}(\omega)}{\sum_{k=1}^K\chi^2_{0,k}}
\end{equation}
and it can easily be shown that the $P_N$ can be constructed as a weighted sum of $P_N^{(k)}$:
\begin{equation}
  P_N(\omega) = \frac{\sum_{k=1}^K\left[\chi^2_{0,k}P_N^{k}\right]}{\sum_{k=1}^K\chi^2_{0,k}}
\end{equation}
where, recall $\chi^2_{0,k}$ is simply the $\chi^2$ of the data in each band about the mean. This tells us how we can construct a particular case of the multi-term periodogram from a weighted sum of periodograms in each band. Here the weights reflect both how many measurements there are in each band, and how poorly those measurements are fit by a simple constant reference model.

@@

\todo{Compare different options of $N_{base}$ and $N_{band}$?}
